%-------------------------
% Resume in LaTeX
% Based on Jake's Resume template
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-3pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%===========================================
\begin{document}

%----------HEADER--------------------------
\begin{center}
    {\Huge \scshape Ender Batu Demirta\c{s}} \\ \vspace{4pt}
    \small
    (307) 301-7092 $|$
    \href{mailto:ba2demirtas@gmail.com}{\underline{ba2demirtas@gmail.com}} $|$
    \href{https://linkedin.com/in/batu-demirtas-ba83812ba/}{\underline{LinkedIn}} $|$
    \href{https://github.com/Batu-end}{\underline{GitHub}} $|$
    Fullerton, CA
\end{center}

%-----------EDUCATION----------------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {California State University, Fullerton}{Fullerton, CA}
    {Bachelor of Science in Computer Science}{May 2026}
    \resumeItemListStart
      \resumeItem{\textbf{Relevant Coursework:} Data Structures, Software Engineering, Operating Systems, OOP, Back-end Development, Machine Learning}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE---------------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Association for Computing Machinery (ACM) -- CSUF}{Fullerton, CA}
    {Artificial Intelligence Board Member}{January 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Led an overhaul of presentation and workshop formats, increasing attendance by \textbf{30\%+}.}
      \resumeItem{Revamped our engagement strategies, growing activity participation from negligible to \textbf{25+ students} in interactive activities.}
      \resumeItem{Contributed to a more dynamic and structured AI and ML learning environment, which is both accessible to beginners while also providing depth for experienced members and learners.}
    \resumeItemListEnd

  \resumeSubheading
    {Data Science \& Machine Learning Club (DSML) -- CSUF}{Fullerton, CA}
    {Vice President}{January 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Lead weekly presentations on core data science and machine learning concepts, combining theory with real-world applications.}
      \resumeItem{Implement live tool demonstrations to showcase practical application of core data science concepts.}
      \resumeItem{Host hybrid sessions to maximize accessibility, maintaining high attendance across both online and in-person audiences.}
      \resumeItem{Design case study-driven curricula using realistic datasets to mirror production machine learning challenges.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------------------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Memoria} $|$ \emph{SwiftUI, SwiftData, Swift Charts, Swift Concurrency, macOS + iOS}}{January 2026 -- Present}
    \resumeItemListStart
      \resumeItem{Built a cross-platform (macOS + iOS) trading journal with a local-first \textbf{SwiftData} architecture, ensuring full offline functionality and data privacy with no cloud dependency for core journaling workflows.}
      \resumeItem{Engineered a custom accounting engine computing per-trade VWAP cost basis, time-weighted return (TWR), and daily \textbf{P\&L} attribution; integrated live market data via a REST API to benchmark portfolio performance against the \textbf{S\&P 500} across configurable timeframes.}
      \resumeItem{Designed a professional analytics suite featuring an interactive equity curve with gesture-driven scrubbing (\textbf{Swift Charts}), a daily \textbf{P\&L} calendar heatmap, and a real-time watchlist with asynchronously fetched sparklines.}
    \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{NL2SQL Analytics Platform} $|$ \emph{Python, FastAPI, Strands Agents, AWS (App Runner, RDS, Secrets Manager)}}{September 2025 -- November 2025}
    \resumeItemListStart
      \resumeItem{Developed an agentic AI chatbot that democratizes data access, enabling non-technical users to query structured PostgreSQL databases using natural language.}
      \resumeItem{Orchestrated AI reasoning and dynamic tool execution via \textbf{Strands Agents} and \textbf{Amazon Bedrock} (Claude 3.5), translating plain English into precise, case-insensitive SQL queries while mitigating hallucinations.}
      \resumeItem{Engineered a robust REST API using \textbf{FastAPI} and \textbf{Pydantic}, securely connecting to AWS RDS by dynamically retrieving credentials from \textbf{AWS Secrets Manager} to ensure security.}
      \resumeItem{Deployed a serverless, containerized backend to \textbf{AWS App Runner} leveraging the Amazon Bedrock AgentCore runtime, establishing an automated CI/CD deployment pipeline directly from GitHub.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming Languages:}{ Python, C++, Swift, SQL} \\
    \textbf{Cloud:}{ AWS (EC2, S3, IAM, Bedrock, KMS, EBS)} \\
    \textbf{Frameworks \& Libraries:}{ FastAPI, SwiftUI, SwiftData, LangGraph} \\
    \textbf{Tools \& Collaboration:}{ Git, GitHub Kanban, Jira, Confluence, Slack} \\
    \textbf{Technical Concepts:}{ Algorithms, Machine Learning, RAG, Agentic AI, APIs}
  }}
\end{itemize}

%-----------LEADERSHIP---------------------
\section{Leadership \& Social Influence}
\resumeSubHeadingListStart
  \resumeSubheading
    {Technical Event Production \& Outreach}{Fullerton, CA}
    {Bridging the Gap Between Students and Industry}{January 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Founded and coordinated a guest speaker series, hosting engineering leaders from companies including AWS to deliver panels on production architectures and data engineering.}
      \resumeItem{Attracted over \textbf{20+ students per session} by promoting interactive discussions on modern cloud and back-end practices.}
      \resumeItem{Facilitated industry networking opportunities to prepare student members for technical interviews and post-grad career pathways.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
